Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-13 ForegroundSimulations/ms.tex

Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed.

@@

>>>>

Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed. We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.

The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection. Here we estimate the attenuation required at specific $k_\parallel$ modes of interest to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.

We define the required attenuation as the ratio: 
\begin{align}
  \Gamma_{k_\parallel}(\tau) &= \frac{P_\textrm{H{\sc i}}(k_\parallel)}{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)},
\end{align}
where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with a Blackman-Harris window function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$.

Fig.~\ref{fig:fg-reflections} shows $\Gamma_{k_\parallel}(\tau)$ (in dB) for selected $k_\parallel$ at 0.08~$h$~Mpc$^{-1}$ (left), 0.1~$h$~Mpc$^{-1}$ (middle), and 0.12~$h$~Mpc$^{-1}$ (right) as a function of delays due to reflections from other antenna spacings. The light, medium and dark shaded curves show $\Gamma_{k_\parallel}(\tau)$ for achromatic, {\it Airy}, and chromatic antenna power patterns respectively. These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by antenna-to-antenna reflections. It is noted that a chromatic simulated power pattern sets the most severe upper limit in all three chosen $k_\parallel$ for delays $\tau < 80$~ns (left), $\tau < 120$~ns (middle), and $\tau < 160$~ns.

@@

The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode. For instance, at $k_\parallel=0.08\,h$~Mpc$^{-1}$, the reflections with delays 70~ns require to be attenuated by at $\gtrsim 85$~dB for the simulated power pattern, $\gtrsim 82$~dB for the {\it Airy} pattern, and $\gtrsim 70$~dB for the achromatic pattern. However, at $k_\parallel=0.1\,h$~Mpc$^{-1}$ for the same delay of reflection, the requirement on attenuation is lowered to $\gtrsim 75$~dB, $\gtrsim 30$~dB and $\gtrsim 22$~dB respectively. If the chosen $k_\parallel$ is instead 0.12~$h$~Mpc$^{-1}$, the required attenuation is further relaxed to $\gtrsim 60$~dB, $\gtrsim 15$~dB and $\gtrsim 15$~dB respectively. This further reinforces the significance of reducing the chromaticity of the antenna power pattern to further relax the constraint on the system to achieve the attenuation required to contain the reflected foreground power from other antennas from contaminating the sensitive EoR H{\sc i} signal modes in the {\it EoR window}.
